% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Jiafeng Li}

\basicInfo{
  \email{jiafengli\_wu@foxmail.com} \textperiodcentered\ 
  \phone{(+86) 180-812-21935} \textperiodcentered\ 
  \href{https://wubeizi.github.io/}{Website: wubeizi.github.io}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Huazhong University of Science and Technology}, Hubei, China}{2025 -- Future}
\textit{MA.Sc} in Computer Science, expected September 2025
\datedsubsection{\textbf{Sichuan University(SCU)}, Sichuan, China}{2021 -- Present}
\textit{B.E.} in Software Engineering

\section{\faUsers\ Project Experience}
\datedsubsection{\textbf{Tea Journey} The 17th Computer Design Competition (2024)}{Sep. 2023 -- Present}
\role{Vue, HTML, JavaScript, CSS, Echarts, D3, AntV}{Team Project}
Brief introduction: Tea culture is an important component of excellent traditional Chinese culture, containing profound Confucianism, Buddhism, and Taoism. China is the hometown of tea, and it is said that the discovery and utilization of tea by Chinese people began in the Shennong era. Tea culture contains rich spiritual and cultural connotations.
\begin{itemize}
  \item Technology: This project is developed using the Vue framework as a whole, mainly using Vue.js for project construction. Some Vue components and technologies such as HTML, CSS, and JavaScript are used to display and layout text, images, cards, steps, and other parts. At the same time, visualization open-source libraries such as Echarts, AntV, and D3.js are used for graphic drawing.
  \item Role: I am mainly responsible for scheme design, technical implementation, literature reading, creative design, data collection and cleaning.
\end{itemize}

\datedsubsection{\textbf{University Analysis and Recommendation System} Summer training project in Sichuan University}{Jul. 2023 -- Aug. 2023}
\role{Java, JavaScript, Servlet, Tomcat}{Team Projects}
Brief introduction: The Smart University Big Data Platform is used to provide users with accurate analysis and recommendations of higher education institutions. The system provides users with information display of all 985/211 universities in China, providing comprehensive comparative analysis and enrollment information analysis among target universities, and realizing the analysis and recommendation function of universities.
\begin{itemize}
  \item Technology: This project mainly uses HTML, CSS, and JavaScript as the front-end development languages and utilizes Echarts visualization tools to complete the backend initiation and deployment in the form of a combination of Servlet and Tomcat.
  \item Role: I am mainly responsible for front-end chart production and front-end and back-end interface design.
\end{itemize}

\datedsubsection{\textbf{Music Player} Summer training project in Sichuan University}{Jul. 2022 -- Aug. 2022}
\role{C, C++}{Team Projects}
Brief introduction: With the widespread use of computers and the rapid development of the mobile phone market, various audio resources are also widely circulated online. When users need multitasking operations, they are greatly affected and bring a lot of inconvenience. For most ordinary users, many functions are useless and useless. Based on this, this project aims to design a simple and pure music player.
\begin{itemize}
  \item Technology: This project is the author’s first formal and complete project, mainly developed in C language. It not only gave the author a deeper understanding of many knowledge points in C language, but also learned a lot of new knowledge. At the same time, the development process involves team collaboration, which is also the first time I have had such a collaborative experience.
  \item Role: I am mainly responsible for writing the playlist module and playback module.
\end{itemize}

% Reference Test
% \datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
% An xxx optimized for xxx\cite{verma2015large}
% \begin{itemize}
%  \item main contribution
% \end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C == HTML > Python > Java
  \item Knowledge: Proficient in machine learning algorithms; competent to software and system development, neural network; understand Windows.
  \item Tool: competent in Latex, Git.
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{1} Comprehensive Scholarship}, Award on Sichuan University}{Sep. 2023}
\datedline{\textit{\nth{2} Provincial Prize}, National College Student Mathematics Competition}{Jun. 2023}
\datedline{\textit{\nth{2} National Prize}, National Simulation Application Competition}{Nov. 2023}
\datedline{\textit{\nth{2} Comprehensive Scholarship}, Award on Sichuan University}{Sep. 2022}
\datedline{\textit{\nth{3} Provincial Prize}, The 13th Blue Bridge Cup National Software and Information Technology Professional Talent Competition}{May. 2022}


\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: https://blog.csdn.net/qq\_62738515?type=blog
  \item GitHub: https://github.com/wubeizi
  \item Languages: English - Fluent, Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
